---
title: "Transformed Testing Data"
author: "Alan Phan"
date: "12/1/2019"
output: html_document
---

---
title: "146 Homework Week 7"
author: "Alan Phan"
date: "11/13/2019"
output:
  html_document: default
  word_document: default
---
```{r echo = T, results = "hide", warning = F}
#load libraries
library(ggplot2)
library(tidyverse)
library(TSA)
library(tseries)
library(dplyr)
```

```{r}
#Load the data
apple <- read.csv("C:/Users/erwu1/Desktop/AAPL_data.csv")
```

```{r}
#Begin cleaning the data to get it ready for a time series analysis
head(apple) #read the data
apple.high <- apple$high #From here we isolate the high variable in order to conduct the time series analysis
apple.high.test <- apple.high[1:1239]
```

```{r}
#Create the time series
apple.test <- ts(apple.high.test)
apple.ts <- ts(apple.high)
#plot the time series
plot(apple.test)
plot(apple.ts)
```

Looking at the time series we can see that the variance is not constant and there is definitely a trend going on. So before we try to fit a model we should first transform the data and attempt to difference it as well

```{r, eval = F}
#BoxCox.ar(y = apple.ts)
```
Using just a normal boxcox with the time series data produces an error however when using the square root of the time series data we get an output
```{r}
BoxCox.ar(sqrt(apple.ts))
```
From the boxcox output we can see that the 1/2 power is viable for the square root of the time series. This means that we should do a 1/4 power on the time series to produce an approximately normal data

```{r}
#Transform the data using the boxcox recommendation
transformed.test <- apple.test^(1/4)
transformed.ts <- apple.ts^(1/4)
#Plot the transformed time series data
plot(transformed.ts)
```

FORECASTING



MA(1)
```{r}
apple.ma.test=arima(transformed.test, order=c(0,1,1),method="ML")
apple.ma.test
```
The ML esitmates are θ = −0.9837, μˆ = 3.2139, sigma^2e = 0.01377, which gives the fitted model
Yt = 3.2139 + et + 0.9837et−1

Here are the MA(1) forecasts for lead times l = 1, 2, · · · 10, computed using the predict function in R:
```{r}
apple.ma.predict<-predict(apple.ma.test,n.ahead=20)
round(apple.ma.predict$pred,3)
```

```{r}
round(apple.ma.predict$se,3)
```

```{r}
# Create lower and upper prediction interval bounds
lower.pi<-apple.ma.predict$pred-qnorm(0.975,0,1)*apple.ma.predict$se
upper.pi<-apple.ma.predict$pred+qnorm(0.975,0,1)*apple.ma.predict$se 
# Display prediction intervals (2007-2026) 
data.frame(Year=c(1240:1259),lower.pi,upper.pi)
```

```{r}
# Original series starts at Year = 2013
# Note: Argument n1=1880 starts plot at 2013
# Note: Argument pch=16 produces a small black circle (for MMSE forecasts)
#apple.ma.test
plot(transformed.ts, pch = 16)
plot(apple.ma.test, n.ahead = 20,ylab="Apple Stock",xlab="Year", col='red', pch=16)
# Put horizontal line at ML estimate of overall mean
#abline(h=coef(apple.ma.test)[names(coef(apple.ma.test))=='intercept']) 
#no abline because intercept = 0
# Put prediction interval lines on plot (darker than default)
lines(y=lower.pi,x=1240:1259,lwd=2,col="red",lty="dashed")
lines(y=upper.pi,x=1240:1259,lwd=2,col="red",lty="dashed")
```
